### 2019-10-21 Manuscript/manuscript.tex
small fixes to references

 An exception to the paucity of published continuous paleogeographic models for the Precambrian is the Neoproterozoic model of \cite{Merdith2017b} which is shown in comparison to the constraints for Laurentia in Figure \ref{fig:Laurentia_paleolatitude}. The extent to which the implied position of Laurentia in \cite{Merdith2017a} is consistent with the compiled paleomagnetic constraints can be visualized in Figure \ref{fig:Laurentia_paleolatitude}. As noted above, the development of such models is challenging and the researchers need to balance varying constraints. The focus here will be on the extent to which this model satisfies the available paleomagnetic poles for Laurentia. The model does not honor the Grenville loop (e.g. go to moderately high southerly latitudes ca. 1000 Ma) which is a striking departure from the paleomagnetic record and standard paleogeographic models. Additionally, the implemented plate motion strays from the younger poles of the Keweenawan Track and does not honor the Franklin LIP pole despite its `A' Nordic rating. The Franklin pole is taken to be a key constraint at the Tonian/Cryogenian boundary that provides evidence of the supercontinent Rodinia being equatorial and for the Sturtian glaciation having extended to equatorial latitudes.

>>>>

 An exception to the paucity of published continuous paleogeographic models for the Precambrian is the Neoproterozoic model of \cite{Merdith2017b} which is shown in comparison to the constraints for Laurentia in Figure \ref{fig:Laurentia_paleolatitude}. The extent to which the implied position of Laurentia in \cite{Merdith2017b}} is consistent with the compiled paleomagnetic constraints can be visualized in Figure \ref{fig:Laurentia_paleolatitude}. As noted above, the development of such models is challenging and the researchers need to balance varying constraints. The focus here will be on the extent to which this model satisfies the available paleomagnetic poles for Laurentia. The model does not honor the Grenville loop (e.g. go to moderately high southerly latitudes ca. 1000 Ma) which is a striking departure from the paleomagnetic record and standard paleogeographic models. Additionally, the implemented plate motion strays from the younger poles of the Keweenawan Track and does not honor the Franklin LIP pole despite its `A' Nordic rating. The Franklin pole is taken to be a key constraint at the Tonian/Cryogenian boundary that provides evidence of the supercontinent Rodinia being equatorial and for the Sturtian glaciation having extended to equatorial latitudes.
